---
title: "Kermit Perceptions Rank-based test"
author: "Anna Calle"
date: "11/13/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

<<<<<<< HEAD
Anna's first meassage in the document.

Try number 2...
=======
Anna's first meassage in the document


```{r}
#Priscilla loading tidyverse and reading in kermit data

library(tidyverse)

kermit <- read_csv("kermit.csv")

```
```{r}
#Prisclla making side by side histograms of Score.pre separated by gender

kermit_hist <-kermit %>% 
  ggplot(aes(x = Score.pre)) +
  geom_histogram(bins = 4) +
  facet_wrap(~Gender)

kermit_hist
```


perform rank based comaprsisons using Mann Whitney U and Wilcoxon sign ranked
Question: Is there a significant differnece in pre-talk ranks of kermit for Male and Female respondents?

```{r}
mwu_kermit <- kermit %>% 
  wilcox.test(Score.pre ~Gender, data = .)

# Null: NO significant difference
# Alternative: there is a significant difference in ranks

mwu_kermit


```

There was no significant difference in ranks for male and female respondents (W = 155.5, p=0.4, alpha = 0.05)

Next questiob: Is there a significant change in Kermit rankings before and after his bren talk

```{r}

#Null: there is not a significant difference in ranks for pre and post talk scores
wsr_kermit <- wilcox.test(kermit$Score.pre, kermit$Score.post, paired = TRUE)

wsr_kermit

```
There is no significant difference in ranks for pre and post talk Kermit scores (statistucal summary here.....)
